Summarize coverage

### 2017-01-02 analysis/summarize_coverage.Rmd
Successfully re-knit summarize_coverage.Rmd after addressing bugs in dsc-shrink-files output.

@@

```{r chunk_options, include=FALSE}
library(dscr)
library(ashr)
library(reshape2)
library(ggplot2)
library(dplyr)
source("chunk-options.R")
```

```{chunk_label r}
load("../output/dsc-shrink-files/res.RData")
coverthresh = 0.05 # threshold at which we look at coverage
findthresh  = 0.95 # threshold at we define a discovery significant

neglong = 
  res$negprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name="negprob") %>%
    filter(negprob > findthresh)

poslong = 
  res$posprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name="posprob") %>%
    filter(posprob > findthresh)

reslong = 
  res$cdf_score %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%    
    melt(id.vars=c("method","scenario","seed",".id"))

reslong.pos = inner_join(reslong,poslong)
reslong.neg = inner_join(reslong,neglong)
dim(reslong.pos)
dim(reslong.neg)

```

@@

Table of lower tail for all observations
```{r}
xtabs(lt~method+scenario,reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh))) %>% round(2)
```

Table of lower tail of positive findings. Because of the unimodal assumption
and the favoritism toward the null this should assess problems
with``over shrinkage" toward 0.
```{r}
xtabs(lt~method+scenario,reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh))) %>% round(2)
```

Table of lower tail of negative findings. This should indicate problems with tail behaviour of $g$. The uniform methods tend to over-shrink.
```{r}
xtabs(lt~method+scenario,reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh))) %>% round(2)
```

```{r}
save_latex_coverage_table=function(df,methodnames,filename,SCENARIONAMES=c("spiky","near-normal","flat-top","skew","big-normal","bimodal"),switch=FALSE){
  library(xtable)
  df$method=factor(df$method,levels=methodnames)
  df$scenario=factor(df$scenario,levels=SCENARIONAMES)
  mat <- as.matrix(xtabs(lt~method+scenario,df))
  if(switch){
    mat=1-mat
  }
  mat <- xtable(mat,digits=rep(2,ncol(mat)+1))
  write(print(mat, 
        sanitize.text.function = function(x){x},
        floating=FALSE, 
        hline.after=NULL, 
        add.to.row=list(pos=list(-1,0, nrow(mat)), 
                        command=c('\\toprule ',
                                  '\\midrule ',
                                  '\\bottomrule '))
      ),file=filename)

}

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/coverage_neg.tex")
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/coverage_pos.tex")
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/coverage_all.tex")

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/coverage_neg_nopen.tex")
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/coverage_pos_nopen.tex")
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/coverage_all_nopen.tex")
```

These tables show 1-the left tail instead of the left tail.
```{r}
save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/scoverage_neg.tex",switch=TRUE)
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/scoverage_pos.tex",switch=TRUE)
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/scoverage_all.tex",switch=TRUE)

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/scoverage_neg_nopen.tex",switch=TRUE)
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/scoverage_pos_nopen.tex",switch=TRUE)
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/scoverage_all_nopen.tex",switch=TRUE)
```

>>>>

Note that rendering this RMarkdown document may take a few minutes because 
it involves loading and processing tables with millions of rows.

@@

```{r chunk_options, include=FALSE}
library(dscr)
library(ashr)
library(reshape2)
library(ggplot2)
library(magrittr)
library(dplyr)
library(xtable)
source("chunk-options.R")
```

Compile the results on the simulated data sets for the summaries below.

```{r compile_tables}
load("../output/dsc-shrink-files/res.RData")
coverthresh = 0.05  # threshold at which we look at coverage
findthresh  = 0.95  # threshold at we define a discovery significant

neglong = 
  res$negprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars = c("method","scenario","seed",".id"),
         value.name = "negprob") %>%
    filter(negprob > findthresh)

poslong = 
  res$posprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars = c("method","scenario","seed",".id"),
         value.name = "posprob") %>%
    filter(posprob > findthresh)

reslong = 
  res$cdf_score %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%    
    melt(id.vars = c("method","scenario","seed",".id"))

reslong.pos = inner_join(reslong,poslong)
reslong.neg = inner_join(reslong,neglong)
```

@@

Table of lower tail for all observations:

```{r table_all_obs}
print(xtabs(lt ~ method + scenario,
            reslong %>% group_by(scenario,method) %>% 
            summarize(lt = mean(value < coverthresh))) %>% round(2))
```

Table of lower tail of positive findings. Because of the unimodal assumption
and the favoritism toward the null, this should assess problems with "over 
shrinkage" toward 0.

```{r table_pos}
print(xtabs(lt ~ method + scenario,
            reslong.pos %>% group_by(scenario,method) %>% 
              summarize(lt = mean(value < coverthresh))) %>% round(2))
```

Table of lower tail of negative findings. This should indicate problems with 
tail behaviour of $g$. The uniform methods tend to over-shrink.

```{r table_neg}
print(xtabs(lt ~ method + scenario,reslong.neg %>% 
            group_by(scenario,method) %>% 
            summarize(lt = mean(value < coverthresh))) %>% round(2))
```

Compile some more summary tables in Latex format.

```{r write_latex_tables}
save_latex_coverage_table = 
  function(df, methodnames, filename,
           SCENARIONAMES = c("spiky","near-normal","flat-top","skew",
                             "big-normal","bimodal"),
           switch = FALSE) {
  df$method   <- factor(df$method,levels = methodnames)
  df$scenario <- factor(df$scenario,levels = SCENARIONAMES)
  mat         <- as.matrix(xtabs(lt~method+scenario,df))
  if (switch)
    mat <- 1 - mat
  mat <- xtable(mat,digits = rep(2,ncol(mat) + 1))
  write(print(mat,sanitize.text.function = function (x) x,
        floating = FALSE,hline.after = NULL, 
        add.to.row = list(pos = list(-1,0,nrow(mat)), 
                          command = c('\\toprule ',
                                      '\\midrule ',
                                      '\\bottomrule '))),file = filename)
}

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n","ash.u","ash.hu"),
                          "table/coverage_neg.tex")
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n","ash.u","ash.hu"),
                          "table/coverage_pos.tex")
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n","ash.u","ash.hu"),
                          "table/coverage_all.tex")
save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n.s","ash.u.s","ash.hu.s"),
                          "table/coverage_neg_nopen.tex")
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n.s","ash.u.s","ash.hu.s"),
                          "table/coverage_pos_nopen.tex")
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n.s","ash.u.s","ash.hu.s"),
                          "table/coverage_all_nopen.tex")
```

These tables show right tail instead of the left tail.

```{r write_latex_tables_right}
save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n","ash.u","ash.hu"),
                          "table/scoverage_neg.tex",switch = TRUE)
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n","ash.u","ash.hu"),
                          "table/scoverage_pos.tex",switch = TRUE)
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n","ash.u","ash.hu"),
                          "table/scoverage_all.tex",switch=TRUE)

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n.s","ash.u.s","ash.hu.s"),
                          "table/scoverage_neg_nopen.tex",switch = TRUE)
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n.s","ash.u.s","ash.hu.s"),
                          "table/scoverage_pos_nopen.tex",switch = TRUE)
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% 
                            summarize(lt = mean(value < coverthresh)),
                          c("ash.n.s","ash.u.s","ash.hu.s"),
                          "table/scoverage_all_nopen.tex",switch = TRUE)
```
